\chapter*{Acknowledgements}
I would like to express my sincere gratitude to my project supervisor, Dr. Niharika Anand, for her invaluable guidance, support, and encouragement throughout the course of this project. Her expertise and insights have been instrumental in shaping the direction and success of this work.\\
I am also grateful to the faculty and staff of the Department of Information Technology at Indian Institute of Information Technology, Lucknow, for providing the necessary resources and a conducive learning environment.\\
Special thanks go to the Züs platform team for their collaboration and support during the integration of the split key wallet protocol and mobile authenticator. Their feedback and assistance have been crucial in ensuring the smooth implementation and testing of the proposed solution. \\
I would like to acknowledge the developers and contributors of the open-source libraries and frameworks used in this project, particularly the Apache Milagro Cryptographic Library and the Android framework. Their efforts and contributions have greatly facilitated the development process.\\
I extend my appreciation to my fellow students and colleagues for their valuable discussions, suggestions, and peer review throughout the project. Their input has helped refine and improve various aspects of the work.\\
Finally, I am deeply grateful to my family and friends for their unwavering support, encouragement, and understanding during the pursuit of this project. Their constant motivation and belief in me have been a source of strength and inspiration.
Thank you all for your contributions and support in making this project a success. \\ \\
\noindent Lucknow \hfill Yash Verma \
\noindent May 2024
\thispagestyle{empty}
\setcounter{page}{3}
